---
title: "P8105_hw1_jl6648"
output: html_document
author: Jixin Li
date: "2023-09-15"
---

## problem 1

```{r}
library(tidyverse)
```


```{r}
library(moderndive)
data("early_january_weather")
mean(early_january_weather$temp)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("early_january_weather.pdf")
```

description of the dataset:

the dataset contains variables including origin, year, month, day, hour, temperature, dewp, humid, wind_dir, wind_speed, wind_gust, precipitation, visib,and time_hour. Among these variables, origin is the character variable, the rest of variables are all quantitative variable. 
the dataset contains 358 number of rows and 15 number of columns 
the mean of temperature is 39.58212. 

description of the scatterplot:
over the time, the temperature went up and down regularly. the overall trends of temperature went up starting from observation date to Jan 14, then the trend of temperature went down back to the temperature at the beginning. over the time, the humid gradually increase. 

## problem 2 

```{r}
problem2_df=
  tibble(
    vec_numeric = rnorm(10),
    vec_logical = vec_numeric > 0,
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_factor = factor(c("high", "medium", "low", "medium", "high", "low",
                        "low", "medium", "high", "high")),
  )
```

```{r}
mean(pull(problem2_df, vec_numeric))
mean(pull(problem2_df, vec_logical))
mean(pull(problem2_df, vec_char))
mean(pull(problem2_df, vec_factor))
```
the mean of vec_numeric and vec_logical works. However, it is not working to take the mean of vec_char and vec_factor

```{r}
as.numeric(pull(problem2_df, vec_logical))
as.numeric(pull(problem2_df, vec_char))
as.numeric(pull(problem2_df, vec_factor))
```

it convert logical, character, and factor vector to numeric variables because only numeric variable has the mean value, which explains you can not take a mean of not numeric variable. 