---
title: "P8105_hw1_jl6648"
output: github_document
author: Jixin Li
date: "2023-09-15"
---

## problem 1

```{r}
library(tidyverse)
```


```{r}
library(moderndive)  #load moderndive 
data("early_january_weather") #load data
mean(early_january_weather$temp) #calculate the mean of temperature 
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
#use ggplot to create scatterplot
ggsave("early_january_weather.pdf") #save the image of scatterplot 
```

description of the dataset:

the dataset contains variables including origin, year, month, day, hour, temperature, dewp, humid, wind_dir, wind_speed, wind_gust, precipitation, visib,and time_hour. Among these variables, origin is the character variable, the rest of variables are all quantitative variable. 
the dataset contains 358 number of rows and 15 number of columns 
the mean of temperature is 39.58212. 

description of the scatterplot:
over the time, the temperature went up and down regularly. the overall trends of temperature went up starting from observation date to Jan 14, then the trend of temperature went down back to the temperature at the beginning. over the time, the humid gradually increase. 

## problem 2 

```{r}
#use tibble to manipulate and print a dateframe
problem2_df=
  tibble( 
    vec_numeric = rnorm(10), #generate random number 
    vec_logical = vec_numeric > 0, #generate a logical vector 
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_factor = factor(c("high", "medium", "low", "medium", "high", "low",
                        "low", "medium", "high", "high")),
  )
#generate character and factor vector 
```

```{r}
#use mean function to take mean of all variables 
mean(pull(problem2_df, vec_numeric))
mean(pull(problem2_df, vec_logical))
mean(pull(problem2_df, vec_char))
mean(pull(problem2_df, vec_factor))
```
the mean of vec_numeric and vec_logical works. However, it is not working to take the mean of vec_char and vec_factor

```{r}
#use as.numeric function convert nonnumeric factor to numeric 
as.numeric(pull(problem2_df, vec_logical))
as.numeric(pull(problem2_df, vec_char))
as.numeric(pull(problem2_df, vec_factor))
```

it convert logical, character, and factor vector to numeric variables because only numeric variable has the mean value, which explains you can not take a mean of not numeric variable. 